Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-08-03 PAPER/main.tex
minor changes to MBR

\begin{definition}
	\label{defn:cop}
	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple. The \emph{Constrained Ordering Problem (COP)} consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
	\begin{equation}
		\label{eqn:vsc}
		\emph{\textbf{rhs}}(i) + \emph{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
	\end{equation}
	where \emph{\textbf{lhs}($i$)} and \emph{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the \emph{vicinal sum constraint}.
\end{definition}
For example, given $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, one possible solution is $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.

@@

Starting from the first edge in the list, BR then searches through the list to find an edge that meets the following conditions: 
\begin{enumerate*}[label={(\alph*)}]
	\item the lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
	\item the current edge and the next edge are members of different components on $G'$.
\end{enumerate*}
If these conditions are met, BR adds the current edge to a set $R_1$, and continues to add all succeeding edges in the list to $R_1$ provided that, for each edge, both conditions hold and the succeeding edge is not a member of a component of $G'$ that has an edge in $R_1$. Once there are no more valid edges available to add to $R_1$, BR resumes its search through the remaining edges in the list to find another edge that meets the conditions, and can begin a new set $R_2$. The procedure terminates once the penultimate edge in the list has been assessed.

@@

\noindent  In the final case above, a Modified Bridge Recognition (MBR) algorithm is used to find suitable overlapping sets. Firstly, a copy of the set $R_i$ with the highest cardinality\footnote{In the event of a tie, MBR selects the set with the lowest index.} generated by BR is created, called $R^{*}_1$, and is added to $\mathcal{R}^{*}$. Then, MBR takes the original sorted list used in BR and removes edges from the list that are already in $\mathcal{R}^{*}$. Similarly to BR, MBR proceeds through the list to find an edge that meets the following conditions:
\begin{enumerate*}[label={(\alph*)}]
	\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
	\item the current edge and an edge in $\mathcal{R}^{*}$ are members of the same component of $G'$, and the next edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, or vice versa.
\end{enumerate*}
If both conditions hold, the current edge is added to a new set $R^{*}_2$ which is then added to $\mathcal{R}^{*}$. MBR continues to add succeeding edges to $R^{*}_2$, provided condition (a) holds and the succeeding edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, stopping when an edge that does not meet these conditions is reached. Then, if every component of $G'$ has an edge in one of the sets in $\mathcal{R}^{*}$, these sets are able to connect all the components of $G'$ together, and so MBR terminates. Otherwise, the edges in $R^{*}_2$ are removed from the sorted list, and MBR repeats the search for suitable edges to start a new set $R^{*}_3$. This procedure continues until either $\mathcal{R}^{*}$ contains overlapping sets that cover all components of $G'$, or until there are no more suitable edges in the list to start a new set. If MBR has produced a feasible collection of sets then the components of $G'$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in $\mathcal{R}^{*}$.

>>>>

\begin{definition}
	\label{defn:cop}
	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers\\ $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple. The \emph{Constrained Ordering Problem (COP)} consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
	\begin{equation}
		\label{eqn:vsc}
		\emph{\textbf{rhs}}(i) + \emph{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
	\end{equation}
	where \emph{\textbf{lhs}($i$)} and \emph{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the \emph{vicinal sum constraint}.
\end{definition}
For example, given $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, one possible solution is $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.

@@

Starting from the first edge in the list, BR then searches through the list to find an edge that meets the following conditions: 
\begin{enumerate*}[label={(\alph*)}]
	\item the lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
	\item the current edge and the next edge are members of different components on $G'$.
\end{enumerate*}
If these conditions are met, BR adds the current edge to a set $R_1$, and continues to add all succeeding edges in the list to $R_1$ provided that, for each edge, both conditions hold and the succeeding edge is not a member of a component of $G'$ that already has an edge in $R_1$. Once there are no more valid edges available to add to $R_1$, BR resumes its search through the remaining edges in the list to find another edge that meets the conditions, and can begin a new set $R_2$. The procedure terminates once the penultimate edge in the list has been assessed.

@@

\noindent  In the final case above, a Modified Bridge Recognition (MBR) algorithm is used to find suitable overlapping sets. Firstly, a copy of the set $R_i$ with the highest cardinality\footnote{In the event of a tie, MBR selects the set with the lowest index.} generated by BR is created, called $R^{*}_1$, and is added to $\mathcal{R}^{*}$. Then, MBR takes the sorted list used in BR and removes edges from the list that are in $\mathcal{R}^{*}$. Similarly to BR, MBR proceeds through the list to find an edge that meets the following conditions:
\begin{enumerate*}[label={(\alph*)}]
	\item the lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
	\item the current edge and an edge in $\mathcal{R}^{*}$ are members of the same component of $G'$, and the next edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, or vice versa.
\end{enumerate*}
If both conditions hold, the current edge is added to a new set $R^{*}_2$ which is then added to $\mathcal{R}^{*}$. MBR continues to add succeeding edges to $R^{*}_2$, provided (a) holds and the succeeding edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$. Then, if every component of $G'$ has an edge in one of the sets in $\mathcal{R}^{*}$, these sets are able to connect all the components of $G'$ together, and so MBR terminates. Otherwise, the edges in $R^{*}_2$ are removed from the sorted list, and MBR repeats the search for suitable edges to start a new set $R^{*}_3$. This procedure continues until either $\mathcal{R}^{*}$ contains overlapping sets that cover all components of $G'$, or until there are no more suitable edges in the list to start a new set. If MBR has produced a feasible collection of sets then the components of $G'$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in $\mathcal{R}^{*}$.
